\section{Executive Summary}

\begin{executivesummary}
\textbf{Decision supported.} This report helps a destination marketing or accommodation portfolio team decide which European countries should receive deeper regional and city-level investigation for shoulder-season platform-tourism opportunities.

\textbf{Scope.} The analysis is a country-level screen using Eurostat platform-tourism data. It is designed to prioritize follow-up analysis, not to allocate campaign budget directly. Marketing and pricing decisions happen at destination and month level, which requires the Phase 2 and Phase 3 work described later in this report.

\textbf{Recommendation.} Prioritize \countrycode{EL}, \countrycode{FR}, \countrycode{IT}, \countrycode{HR}, and \countrycode{ES} for Phase 2 regional analysis. These countries are the strongest candidates because they combine demand scale, growth, and/or summer concentration in ways that justify further data acquisition.

\textbf{Next decision.} Phase 2 should answer which regions inside the shortlisted countries deserve city-level data acquisition. Phase 3 should produce a city-month investment score.
\end{executivesummary}

\begin{tcbitemize}[raster columns=3,raster equal height,raster column skip=3mm]
  \tcbitem[colback=VMIPaper,colframe=VMIGold]
  {\sffamily\small\bfseries\color{VMIWarmGray}Country shortlist}\par
  {\sffamily\Large\bfseries\color{VMIBurgundy}EL, FR, IT, HR, ES}\par
  {\footnotesize\color{VMIWarmGray}Countries prioritized for regional follow-up.}

  \tcbitem[colback=VMIPaper,colframe=VMIGold]
  {\sffamily\small\bfseries\color{VMIWarmGray}Decision type}\par
  {\sffamily\Large\bfseries\color{VMIBurgundy}Screening}\par
  {\footnotesize\color{VMIWarmGray}This is not yet a campaign-deployment model.}

  \tcbitem[colback=VMIPaper,colframe=VMIGold]
  {\sffamily\small\bfseries\color{VMIWarmGray}Current release}\par
  {\sffamily\Large\bfseries\color{VMIBurgundy}v0.2.0}\par
  {\footnotesize\color{VMIWarmGray}Country Screening Release.}
\end{tcbitemize}

\begin{recommendation}
Fund a focused Phase 2 analysis on the five shortlisted countries before any campaign or pricing budget is allocated. The country score identifies where deeper analysis is justified first; it does not imply that countries outside the shortlist have no opportunity.
\end{recommendation}
