\section{Business Context and Scope}

The original business question is where shoulder-season marketing or pricing effort could generate value in European platform tourism. At country level, that question cannot be answered directly. A campaign targets a destination and time window, not an entire country in aggregate. For example, the relevant decision is closer to ``Athens in April'' or ``Dubrovnik in September'' than to ``Greece'' or ``Croatia'' as a whole.

The country screen is therefore an upstream decision layer. It identifies which countries justify the cost of acquiring and validating finer geographic data.

\begin{decision}
\textbf{Phase 1 decision.} Which European countries should be prioritized for regional and city-level follow-up analysis?
\end{decision}

\subsection{Scope rationale}

Phase 1 screens the available European country panel. Phase 2 intentionally narrows deeper analysis to the top-ranked shortlisted countries. This is a release-scope decision: regional and city-level analysis introduces additional data acquisition, geographic joins, validation work, and local-market interpretation. Applying that full workflow to every European country would make the project broader but not necessarily more decision-ready.

The objective of this portfolio release is to demonstrate a reproducible decision framework on a focused, high-signal subset. Countries outside the shortlist remain part of the Phase 1 benchmark and can be added in later releases if the framework is expanded.

\subsection{Method in brief}

The country opportunity score combines three normalized signals:

\begin{itemize}
  \item \textbf{Demand level}: recent mean annual platform nights, log-scaled to prevent the largest markets from fully dominating the score.
  \item \textbf{Growth}: recent growth versus a prior baseline.
  \item \textbf{Seasonality concentration}: summer peak concentration as a signal of potential shoulder-season redistribution.
\end{itemize}

\begin{methodnote}
The default country score is \(0.45\times\text{demand level} + 0.30\times\text{growth} + 0.25\times\text{seasonality concentration}\). The score is ordinal and directional. It ranks countries for follow-up investigation; it is not an uplift estimate, forecast, or causal model.
\end{methodnote}

\subsection{Decision boundary}

\begin{limitation}
This report should not be used to allocate campaign budget directly. It should be used to decide where to invest in Phase 2 regional analysis and Phase 3 city-level investment scoring.
\end{limitation}
